Stimuli List Generation

### 2023-03-05 Stimuli List and Data Source/List Generation.Rmd
added practiceTrials variable to phrase lists and data source

List_1_New <- dplyr::full_join(Practice_trials, Phrase_List_1_random) %>%
  dplyr::relocate(., targetPhrase, .after = speaker) %>%
  dplyr::relocate(., code, .before = speaker) %>%
  #creating new trial number, block number, and counter balance variables
  dplyr::mutate(., trial = row_number(),
                counterBalance = 1,
                block = ifelse(speaker == "Practice", 1, ceiling((row_number() - 5)/ 10) + 1)) %>%
  #moving trial and block variables in the data frame
  dplyr::relocate(trial, .before = code) %>%
  dplyr::relocate(block, .before = counterBalance)

@@

List_2_New <- dplyr::full_join(Practice_trials, Phrase_List_2_random) %>%
  dplyr::relocate(., targetPhrase, .after = speaker) %>%
  dplyr::relocate(., code, .before = speaker) %>%
  #creating new trial, block number, and counter balance variables
  dplyr::mutate(., trial = row_number(),
                counterBalance = 2,
                block = ifelse(speaker == "Practice", 1, ceiling((row_number() - 5) /10) + 1)) %>%
  # relocating trial and block variables in data frame
  dplyr::relocate(trial, .before = code) %>%
  dplyr::relocate(block, .before = counterBalance)

>>>>

List_1_New <- dplyr::full_join(Practice_trials, Phrase_List_1_random) %>%
  dplyr::relocate(., targetPhrase, .after = speaker) %>%
  dplyr::relocate(., code, .before = speaker) %>%
  #creating new trial number, block number, and counter balance variables
  dplyr::mutate(., trial = row_number(),
                counterBalance = 1,
                block = ifelse(speaker == "Practice", 1, ceiling((row_number() - 5)/ 10) + 1),
                practiceTrial = ifelse(speaker == "Practice", "Practice", "Experimental")) %>%
  #moving new variables in the data frame
  dplyr::relocate(trial, .before = code) %>%
  dplyr::relocate(block, .before = counterBalance) %>%
  dplyr::relocate(practiceTrial, .after = targetPhrase)

@@

List_2_New <- dplyr::full_join(Practice_trials, Phrase_List_2_random) %>%
  dplyr::relocate(., targetPhrase, .after = speaker) %>%
  dplyr::relocate(., code, .before = speaker) %>%
  #creating new trial, block number, and counter balance variables
  dplyr::mutate(., trial = row_number(),
                counterBalance = 2,
                block = ifelse(speaker == "Practice", 1, ceiling((row_number() - 5) /10) + 1),
                practiceTrial = ifelse(speaker == "Practice", "Practice", "Experimental")) %>%
  # relocating new variables in data frame
  dplyr::relocate(trial, .before = code) %>%
  dplyr::relocate(block, .before = counterBalance) %>%
  dplyr::relocate(practiceTrial, .after = targetPhrase)
